Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-11-02 paper-webserver.tex
ADD: reference virulencefinder

% 2. Big Problem: but tools are for individual analysis
The rapid characterization and comparison of bacterial pathogens relies principally on the combination of outputs from multiple software programs that are targeted for specific applications. Examples include the Resistance Gene Identifier (RGI) \cite{mcarthur2013comprehensive} for antimicrobial resistance (AMR) gene prediction, Prokka for bacterial genome annotation \cite{doi:10.1093/bioinformatics/btu153}, and {ANOTHER EXAMPLE}. Comprehensive platforms that combine individual programs into a cohesive whole also exist. These include free platforms such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial}, the Integrated Rapid Infectious Disease Analysis (IRIDA) project \url{http://www.irida.ca/}, and PATRIC. Commercial applications, such as Bionumerics, which is used by PulseNet international for the analyses of WGS data in outbreak situations also exist, and offer support as well as accredited, standardized tests {REF}.

>>>>

% 2. Big Problem: but tools are for individual analysis
The rapid characterization and comparison of bacterial pathogens relies principally on the combination of outputs from multiple software programs that are targeted for specific applications. Examples include the Resistance Gene Identifier (RGI) \cite{mcarthur2013comprehensive} for antimicrobial resistance (AMR) gene prediction, VirulenceFinder \cite{kleinheinz2014applying} virulence gene annotation, and Prokka for bacterial genome annotation with external tools \cite{doi:10.1093/bioinformatics/btu153}. Comprehensive platforms that combine individual programs into a cohesive whole also exist. These include free platforms such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial}, the Integrated Rapid Infectious Disease Analysis (IRIDA) project \url{http://www.irida.ca/}, and PATRIC. Commercial applications, such as Bionumerics, which is used by PulseNet international for the analyses of WGS data in outbreak situations also exist, and offer support as well as accredited, standardized tests {REF}.
